Place of death in NRS COVID-19 deaths: data processing for analysis, 2022 data

### 2023-01-17 covid_nrs_place_of_death_data_2022.Rmd
started modifying 2022 code to work with 2023; I'll just make a new file instead

weekly_deaths_overall <-
  ods_raw %>%
  make_human_readable_ref_area %>%
  clean_names() %>%
  ## below series of rename operations are a stupid way of dealing with the possibility of different variable name conventions in the ods_dataset data: sometimes they are in snake_case, and sometimes in camelCase, seemingly unpredictably
  rename_at(.vars = vars(matches("location", ignore.case = TRUE)), ~"place_of_death") %>%
  rename_at(.vars = vars(matches("period", ignore.case = TRUE)), ~"ref_period") %>%
  rename_at(.vars = vars(matches("area", ignore.case = TRUE)), ~"ref_area") %>%
  rename_at(.vars = vars(matches("measure", ignore.case = TRUE)), ~"measure_type") %>%
  rename_at(.vars = vars(matches("cause", ignore.case = TRUE)), ~"cause_of_death") %>%
  rename_at(.vars = vars(matches("sex", ignore.case = TRUE)), ~"sex") %>%
  rename_at(.vars = vars(matches("age", ignore.case = TRUE)), ~"age") %>%
  rename_at(.vars = vars(matches("value", ignore.case = TRUE)), ~"number_of_deaths") %>%  # rename so it's consistent with other data
  filter(!ref_period %in% as.character(2020:2023)) %>% # remove totals for 2020, 2021, 2022, we only want the weekly figures
  parse_ref_period() %>%
  mutate(
    number_of_deaths = as.numeric(number_of_deaths),  # convert to numeric!
  ) %>%
  select(-c(measure_type)) %>%  #  measure_type is count for all data
  recode_place_of_death() %>%
  recode_cause_of_death() %>%
  recalculate_number_of_deaths_after_recoding_cause_of_death %>%  # not needed here probably, but no harm in including it
  pivot_wider(names_from = cause_of_death, values_from = number_of_deaths) %>%  # this dataset is well-formatted and has no implicit missing values!
  mutate(deaths_non_covid = deaths_all_causes - deaths_covid_related)  # compute non-covid deaths from the other two figures - will be NA where either is missing
```

>>>>

weekly_deaths_overall <-
  ods_raw %>%
  make_human_readable_ref_area %>%
  clean_names() %>%
  ## below series of rename operations are a stupid way of dealing with the possibility of different variable name conventions in the ods_dataset data: sometimes they are in snake_case, and sometimes in camelCase, seemingly unpredictably
  rename_at(.vars = vars(matches("location", ignore.case = TRUE)), ~"place_of_death") %>%
  rename_at(.vars = vars(matches("period", ignore.case = TRUE)), ~"ref_period") %>%
  rename_at(.vars = vars(matches("area", ignore.case = TRUE)), ~"ref_area") %>%
  rename_at(.vars = vars(matches("measure", ignore.case = TRUE)), ~"measure_type") %>%
  rename_at(.vars = vars(matches("cause", ignore.case = TRUE)), ~"cause_of_death") %>%
  rename_at(.vars = vars(matches("sex", ignore.case = TRUE)), ~"sex") %>%
  rename_at(.vars = vars(matches("age", ignore.case = TRUE)), ~"age") %>%
  rename_at(.vars = vars(matches("value", ignore.case = TRUE)), ~"number_of_deaths") %>%  # rename so it's consistent with other data
  filter(!ref_period %in% as.character(2020:2029)) %>% # remove totals for 2020, 2021, 2022, etc., we only want the weekly figures
  parse_ref_period() %>%
  mutate(
    number_of_deaths = as.numeric(number_of_deaths),  # convert to numeric!
  ) %>%
  select(-c(measure_type)) %>%  #  measure_type is count for all data
  recode_place_of_death() %>%
  recode_cause_of_death() %>%
  recalculate_number_of_deaths_after_recoding_cause_of_death %>%  # not needed here probably, but no harm in including it
  pivot_wider(names_from = cause_of_death, values_from = number_of_deaths) %>%  # this dataset is well-formatted and has no implicit missing values!
  mutate(deaths_non_covid = deaths_all_causes - deaths_covid_related)  # compute non-covid deaths from the other two figures - will be NA where either is missing
```
